---
title: Making sense of Group F
author: ''
date: '2021-06-19'
slug: making-sense-of-group-f
categories: []
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2021-06-19T21:05:04+02:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

A brace of own goals put an imprortant question to rest. There are already more own goals in this championship than the previous, so 30 points are awarded to the 7 individuals that predicted this outcome. Smugness is probably in order, as the rest of us must work on our excuses. 

```{r init, echo=FALSE, message=FALSE , warning=FALSE}

library(tidyverse)
library(igraph)
library(readxl)
library(knitr)

knitr::opts_chunk$set(out.width = "100%")

```

Group F, the group of death + Hungary, does not dissapoint. Hungary came dead to the championship but refuse flat out to lie down. Germany beat Portugal. This group is wide open.

Our competition is also open, but Sebastian and Scott remain well ahead. The gap between them is now 12 points. Miroslav remains thrird, despite dropping 25 points, with myself and Martin not far behind. At the current pace, though, we will be overtaken by Jacob and Robert. 

```{r graph, echo = FALSE, warning=FALSE,  fig.height=10, fig.width=10}

nettverk <- read.csv("res23.csv", sep = ";", header = FALSE )

leaderboard <- tibble::as_tibble(nettverk)

leaderboard <- leaderboard %>% arrange_at(ncol(.), desc)

hbar<-leaderboard 
hbar$diff<-hbar$V24-hbar$V22

ggplot(hbar, aes(x=reorder(V1, V24), y=V24, fill = diff )) + 
    geom_bar(stat = 'identity') + 
    scale_y_continuous(limits = c(-5, 405)) +
    coord_flip() + 
    scale_fill_gradient2(low = "red", high="blue") +
    geom_text(aes(label = V24), hjust=-0.75, size = 5 ) + 
    ylab("Points") +
    xlab(" ") +
    theme(axis.text=element_text(size=18), axis.title=element_text(size=18,face="bold"))

```