---
title: Can it be Italy this year?
author: HS
date: '2021-06-17'
slug: can-it-be-italy-this-year
categories:
  - Game
tags:
  - Euro2021
subtitle: ''
summary: ''
authors: []
lastmod: '2021-06-17T15:13:34+02:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

```{r init, echo=FALSE, message=FALSE , warning=FALSE}

library(tidyverse)
library(igraph)
library(readxl)
library(knitr)

knitr::opts_chunk$set(out.width = "100%")

```

Øyvind, Jonathan, Marina, Philipp B and Philipp L. have all Italy as champions. At the moment, this outcome looks quite likely. They are already through to the next round as the first team. 

Yesterday's game was so highly anticipated that it made little impact on the standings. Sebastian widened the gap with two points as he was closer to the result than Scott. 

A special shout out to Tor for getting the result spot on.

```{r graph, echo = FALSE, warning=FALSE,  fig.height=10, fig.width=10}

nettverk <- read.csv("res15.csv", sep = ";", header = FALSE )

leaderboard <- tibble::as_tibble(nettverk)

leaderboard <- leaderboard %>% arrange_at(ncol(.), desc)

hbar<-leaderboard 
hbar$diff<-hbar$V16-hbar$V15

ggplot(hbar, aes(x=reorder(V1, V16), y=V16, fill = diff )) + 
    geom_bar(stat = 'identity') + 
    scale_y_continuous(limits = c(-5, 325)) +
    coord_flip() + 
    scale_fill_gradient2(low = "red", high="blue") +
    geom_text(aes(label = V16), hjust=-0.75, size = 5 ) + 
    ylab("Points") +
    xlab(" ") +
    theme(axis.text=element_text(size=18), axis.title=element_text(size=18,face="bold"))

```