---
title: Spain - Poland
author: HS
date: '2021-06-19'
slug: spain-poland
categories:
  - Game
tags:
  - Euro2021
subtitle: ''
summary: ''
authors: []
lastmod: '2021-06-19T23:30:39+02:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

A brace of own goals put an imprortant question to rest. There are already more own goals in this championship than the previous, so 30 points are awarded to the 7 individuals that predicted this outcome. Smugness is probably in order, as the rest of us must work on our excuses. 

```{r init, echo=FALSE, message=FALSE , warning=FALSE}

library(tidyverse)
library(igraph)
library(readxl)
library(knitr)

knitr::opts_chunk$set(out.width = "100%")

```

The color Blue. 

Five individuals had a draw in this game, and are greatly rewarded. Three of these are permanent members of the STV betting committee. It is sometimes hard to phantom why we don't win money more often.

The rest of us can forget about this game altogether.


```{r graph, echo = FALSE, warning=FALSE,  fig.height=10, fig.width=10}

nettverk <- read.csv("res24.csv", sep = ";", header = FALSE )

leaderboard <- tibble::as_tibble(nettverk)

leaderboard <- leaderboard %>% arrange_at(ncol(.), desc)

hbar<-leaderboard 
hbar$diff<-hbar$V25-hbar$V24

ggplot(hbar, aes(x=reorder(V1, V25), y=V25, fill = diff )) + 
    geom_bar(stat = 'identity') + 
    scale_y_continuous(limits = c(-5, 405)) +
    coord_flip() + 
    scale_fill_gradient2(low = "red", high="blue") +
    geom_text(aes(label = V25), hjust=-0.75, size = 5 ) + 
    ylab("Points") +
    xlab(" ") +
    theme(axis.text=element_text(size=18), axis.title=element_text(size=18,face="bold"))

```