---
title: Monday, two out of three games
author: HS
date: '2021-06-14'
slug: monday-two-out-of-three-games
categories:
  - Game
tags:
  - Euro2021
subtitle: ''
summary: ''
authors: []
lastmod: '2021-06-14T21:40:21+02:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---


```{r init, echo=FALSE, message=FALSE , warning=FALSE}

library(tidyverse)
library(igraph)
library(readxl)
library(knitr)

knitr::opts_chunk$set(out.width = "100%")

```

We did not see that coming.

```{r graph, echo = FALSE, warning=FALSE,  fig.height=10, fig.width=10}

nettverk <- read.csv("res9.csv", sep = ";", header = FALSE )

leaderboard <- tibble::as_tibble(nettverk)

leaderboard <- leaderboard %>% arrange_at(ncol(.), desc)

hbar<-leaderboard 
hbar$diff<-hbar$V10-hbar$V8

ggplot(hbar, aes(x=reorder(V1, V10), y=V10, fill = diff )) + 
    geom_bar(stat = 'identity') + 
    scale_y_continuous(limits = c(-5, 220)) +
    coord_flip() + 
    scale_fill_gradient2(low = "red", high="blue") +
    geom_text(aes(label = V10), hjust=-0.75, size = 5 ) + 
    ylab("Points") +
    xlab(" ") +
    theme(axis.text=element_text(size=18), axis.title=element_text(size=18,face="bold"))

```

Both games so far today were rather surprising to most of us. We are collectively in the red, but eight has reason to be happy, and Sebastian has reason to be smug. 

Sebastian did rather well yesterday as well, but was not in the top ten, and was trailing Scott by 32 points. A whopping 39 points from two games where most of us lost points means that the table has turned, and Scott is now in fourth, 14 points behind. 

Miroslav remains in second, after a comparatively good afternoon, with Øyvind right behind. Philipp L. and Marina are also less than a game behind the throne.

Marit has done tremendously well recently and climbed 12 places in a massive jump.

## Stats

So far, we have one own goal, 15 yellow cards, no red cards and 24 goals. Not very interesting so far


