---
title: End of the group stage
author: HS
date: '2021-06-24'
slug: end-of-the-group-stage
categories:
  - Game
tags:
  - Euro2021
subtitle: ''
summary: ''
authors: []
lastmod: '2021-06-24T00:18:59+02:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

```{r init, echo=FALSE, message=FALSE , warning=FALSE}

library(tidyverse)
library(igraph)
library(readxl)
library(knitr)

knitr::opts_chunk$set(out.width = "100%")

```


The group stage is over, and points for the first matches of the knockout stage are distributed. But first, let us review the final games in Group F.

```{r graph, echo = FALSE, warning=FALSE,  fig.height=10, fig.width=10}

nettverk <- read.csv("res36.csv", sep = ";", header = FALSE )

leaderboard <- tibble::as_tibble(nettverk)

leaderboard <- leaderboard %>% arrange_at(ncol(.), desc)

hbar<-leaderboard 
hbar$diff<-hbar$V37-hbar$V35

ggplot(hbar, aes(x=reorder(V1, V37), y=V37, fill = diff )) + 
    geom_bar(stat = 'identity') + 
    scale_y_continuous(limits = c(-5, 645)) +
    coord_flip() + 
    scale_fill_gradient2(low = "red", high="blue") +
    geom_text(aes(label = V37), hjust=-0.75, size = 5 ) + 
    ylab("Points") +
    xlab(" ") +
    theme(axis.text=element_text(size=18), axis.title=element_text(size=18,face="bold"))

```
Two times two - two was not what we had in mind, except for Jon. Both Scott and Sebastian had a bit of bummer this evening, but remain aloof the crowds. First among equals is actually me, but within the 30 point range of a single qualitative question are Jacob, Miroslav and Anna. 

But this is not the current standing, because we do have the points for the first eight knockout games.


```{r knock_64, echo = FALSE, warning=FALSE,  fig.height=10, fig.width=10}
poeng_prev <- tbl_df(read.csv("details36.csv", sep=";", header = FALSE))
poeng_prev$total_prev <- poeng_prev$V2 + poeng_prev$V3 + poeng_prev$V4
poeng_prev <- poeng_prev %>% select(V1, total_prev)

poeng <- tbl_df(read.csv("details36.csv", sep=";", header = FALSE))

poeng$total <- poeng$V2 + poeng$V3 + poeng$V4

poeng <- inner_join(poeng, poeng_prev, by="V1")
poeng$diff <- poeng$total - poeng$total_prev

poeng <- rename(poeng, V35 = V4)
poeng <- rename(poeng, V34 = V3)
poeng <- rename(poeng, V36 = V2)
poeng$V34 <-poeng$V34 - poeng$diff


long_pong <- poeng %>% select(V1, V34, V35, V36, total, diff)  %>% gather(key = V, -V1, -total, value = poeng) %>% arrange(V)

ggplot(data = long_pong, aes(x = reorder(V1, total), y=poeng, fill = V)) + 
  geom_bar(stat = "identity") +
  coord_flip() +
  geom_text(aes(V1, 0, label = total), hjust = -0.50, size = 5) +
  ylab("Points") +
  xlab(" ") +
  scale_fill_manual(values=c("#AAAAAA", "#999999", "#E69F00", "#56B4E9"), 
                    name="Origin",
                    breaks=c("V36", "V35", "V34", "diff"),
                    labels=c("Group Stage", "Qualitative", "Knockout Stage", "Since Last")) +
  theme(axis.text=element_text(size=18), axis.title=element_text(size=18,face="bold")) +
  theme(legend.title=element_text(size=18), 
    legend.text=element_text(size=18))

```
Scott is in the lead, with a 21 point margin! 

This graph consists of four colors. The light gray is the points acquired from the group stage, which will not change. The dark gray is the points from the qualitative questions, of which very few are distributed so far. The orange color are the points from the knockout stage, of which there are plenty to be had. 

In the next updates a light blue color will represent the added points since the last game. 

# Top Scorer

Ronaldo is now the sole top scorer, a predictable outcome only predicted by Jonathan.