---
title: The End
author: HS
date: '2021-07-13'
slug: the-end
categories:
  - Descriptives
tags:
  - Euro2021
subtitle: ''
summary: ''
authors: []
lastmod: '2021-07-13T10:10:25+02:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

```{r init, echo=FALSE, message=FALSE , warning=FALSE}

library(tidyverse)
library(igraph)
library(readxl)
library(knitr)

knitr::opts_chunk$set(out.width = "100%")

```

# The winner is Øyvind Colbjørnsen!

Italy's victory changed quite a lot, and a string of qualitative points provided a solid reshuffle as well. The top three, Øyvind, Philipp L. and Marina, correctly predicted Italy's win. Well done!

Øyvind won with a margin of 37 points, which corresponds to more than one correct answer. Phillip beat Marina with a most slim margin of 10 points. 

Scott and Sebastian had a very thight race up until the final, but Scott ended up 56 points ahead of Sebastian.

```{r knock_64, echo = FALSE, warning=FALSE,  fig.height=10, fig.width=10}
poeng_prev <- tbl_df(read.csv("details50.csv", sep=";", header = FALSE))
poeng_prev$total_prev <- poeng_prev$V2 + poeng_prev$V3 + poeng_prev$V4
poeng_prev <- poeng_prev %>% select(V1, total_prev)

poeng <- tbl_df(read.csv("details50.csv", sep=";", header = FALSE))

poeng$total <- poeng$V2 + poeng$V3 + poeng$V4

poeng <- inner_join(poeng, poeng_prev, by="V1")
poeng$diff <- poeng$total - poeng$total_prev

poeng <- rename(poeng, V35 = V4)
poeng <- rename(poeng, V34 = V3)
poeng <- rename(poeng, V36 = V2)
poeng$V34 <-poeng$V34 - poeng$diff


long_pong <- poeng %>% select(V1, V34, V35, V36, total, diff)  %>% gather(key = V, -V1, -total, value = poeng) %>% arrange(V)

ggplot(data = long_pong, aes(x = reorder(V1, total), y=poeng, fill = V)) + 
  geom_bar(stat = "identity") +
  coord_flip() +
  geom_text(aes(V1, 0, label = total), hjust = -0.50, size = 5) +
  ylab("Points") +
  xlab(" ") +
  scale_fill_manual(values=c("#AAAAAA", "#999999", "#E69F00", "#56B4E9"), 
                    name="Origin",
                    breaks=c("V36", "V35", "V34", "diff"),
                    labels=c("Group Stage", "Qualitative", "Knockout Stage", "Since Last")) +
  theme(axis.text=element_text(size=18), axis.title=element_text(size=18,face="bold")) +
  theme(legend.title=element_text(size=18), 
    legend.text=element_text(size=18))

```
The qualitative part was won by Elin and Marina, both scoring 240 points! Øyvind, Øivind, Jacob, Philipp L., Robert, Leif Erlend and Jostein got 210 points.  

