---
title: Austria and the Netherlands are through
author: HS
date: '2021-06-21'
slug: austria-and-the-netherlands-are-through
categories:
  - Game
tags:
  - Euro2021
subtitle: ''
summary: ''
authors: []
lastmod: '2021-06-21T21:47:29+02:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---


North Macedonia and Ukraine are out.

```{r init, echo=FALSE, message=FALSE , warning=FALSE}

library(tidyverse)
library(igraph)
library(readxl)
library(knitr)

knitr::opts_chunk$set(out.width = "100%")

```

Austria are through, to face everyone's favorites Italy. The Dutch will, at the time of writing, meet Portugal. In their deams, they will meet Hungary, but that looks unlikely. 

```{r graph, echo = FALSE, warning=FALSE,  fig.height=10, fig.width=10}

nettverk <- read.csv("res28.csv", sep = ";", header = FALSE )

leaderboard <- tibble::as_tibble(nettverk)

leaderboard <- leaderboard %>% arrange_at(ncol(.), desc)

hbar<-leaderboard 
hbar$diff<-hbar$V29-hbar$V27

ggplot(hbar, aes(x=reorder(V1, V29), y=V29, fill = diff )) + 
    geom_bar(stat = 'identity') + 
    scale_y_continuous(limits = c(-5, 550)) +
    coord_flip() + 
    scale_fill_gradient2(low = "red", high="blue") +
    geom_text(aes(label = V29), hjust=-0.75, size = 5 ) + 
    ylab("Points") +
    xlab(" ") +
    theme(axis.text=element_text(size=18), axis.title=element_text(size=18,face="bold"))

```

Sebastian is now 10 points ahead of Scott. 10 points. Scott nailed both of these games 100%.

The gap down keeps on growing, as the top pursuers keep on dropping points. 

More to follow shortly.

## Top Scorer

Wijnaldum is co-top scorer with 3 goals. 