---
title: Italy and Wales are through
author: HS
date: '2021-06-20'
slug: italy-and-wales-are-through
categories:
  - Game
tags:
  - Euro2021
subtitle: ''
summary: ''
authors: []
lastmod: '2021-06-20T21:39:57+02:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
---

Italy and Wales are through to the knockout stage. Switzerland could go through as one of the better third placed teams. This fact should in a perfect world lead to the distribution of the first points from the knockout stage, but these will have to wait until the conclusion of the group stage. 

```{r init, echo=FALSE, message=FALSE , warning=FALSE}

library(tidyverse)
library(igraph)
library(readxl)
library(knitr)

knitr::opts_chunk$set(out.width = "100%")

```

Sebastian and Scott are now run-away leaders. Sebastian is a stunning 70 points ahead of Jacob. The gap to Scott has increased to 14 points. 

Marina, Jan Erling and Linda deserve praise for an evening well predicted.

The Welsh got a red card, which brings the tally up to two. 

```{r graph, echo = FALSE, warning=FALSE,  fig.height=10, fig.width=10}

nettverk <- read.csv("res26.csv", sep = ";", header = FALSE )

leaderboard <- tibble::as_tibble(nettverk)

leaderboard <- leaderboard %>% arrange_at(ncol(.), desc)

hbar<-leaderboard 
hbar$diff<-hbar$V27-hbar$V25

ggplot(hbar, aes(x=reorder(V1, V27), y=V27, fill = diff )) + 
    geom_bar(stat = 'identity') + 
    scale_y_continuous(limits = c(-5, 460)) +
    coord_flip() + 
    scale_fill_gradient2(low = "red", high="blue") +
    geom_text(aes(label = V27), hjust=-0.75, size = 5 ) + 
    ylab("Points") +
    xlab(" ") +
    theme(axis.text=element_text(size=18), axis.title=element_text(size=18,face="bold"))

```